Generality in food webs scales with species richness, not latitude

### 2015-04-07 manuscript/latitudepaper.tex
Updated results, still need to apply betas

The effect of latitude on scaling relationships with $S$ varied across
ecosystem types. The strength of scaling decreased towards the poles for $Z$,
$G$, and $V$ in lake food webs, while in stream food webs $G$ increased
towards the poles but $Z$ and $V$ were unaffected (Figs.~\ref{LS,Gen,Vul}).
In all other ecosystem types, the strength of scaling of $Z$, $G$, and $V$
with $S$ did not vary over latitude. These trends were all robust to the
removal of outliers. When scaling relationships were broken down across
trophic levels, however, the situation was more complex. Scaling relationships
with $B$, $I$, and $T$ generally did not follow the pattern set by scaling
relationships with $S$.

[[Need to find a way to express the total effect of all the alphas for a given ecotype...]]
[[Perhaps with a nice table to refer to?]]

[[redo the other paragraphs something like this]]
For example, while $V$ increased with $S$ across all ecosystem types, $V$
tended to decrease with increasing $B$ and $I$ (Fig.~\ref{LS}). The scaling of
$V$ with $B$ was stronger towards the poles in estuarine, lake, and stream
food webs ($\alpha_{Latitude}$=-0.007, $p$=0.006), stronger towards the
equator in terrestrial webs ($\alpha_{Latitude:Terrestrial}$=0.013,
$p$=0.002), and weakly related to latitude in marine webs
($\alpha_{Latitude:Marine}$=0.009, $p$=0.047). Scaling of $V$ with $T$ was
also stronger towards the equator in terrestrial webs
($\alpha_{Latitude:Terrestrial}$=0.006, $p$=0.067,
$\alpha_{Terrestrial}$=-0.093, $p$0.526), while scaling of $V$ with $T$ did
not vary significantly over latitude in estuarine, marine or lake webs
($\alpha_{Latitude}$=-0.001, $p$=0.52). Contrary to the scaling of $V$ with
$B$, scaling of $V$ with $T$ in streams was stronger towards the equator
($\alpha_{Latitude:Stream}$=0.015, $p$\textless0.001,
$\alpha_{Stream}$=-0.822,$p$\textless0.001).

The scaling of $G$ with $S$ folowed a somewhat similar pattern to the scaling
of $Z$ with $S$.  Scaling was slightly stronger towards the equator in
estuarine, marine, and terrestrial food webs ($\alpha_{Latitude}$=-0.001,
$p$=0.363) but stronger towards the poles in lake and stream food webs
($\alpha_{Latitude:Lake}$=0.005, $p$=0.002 and
$\alpha_{Latitude:Stream}$=0.007, $p$=0.002).  The scaling of $G$ with the
proportion of basal resources was stronger towards the poles in estuarine,
stream, and lake food webs ($\alpha_{Latitude}$=-0.009, $p$=0.002) but this
trend was reversed for terrestrial and marine webs
($\alpha_{Latitude:Marine}$=0.011, $p$=0.028;
$\alpha_{Latitude:Terrestrial}$=0.015, $p$=0.001). Similarly, the scaling of
$G$ with the proportion of intermediate consumers was stronger towards the
equator in [[The picture doesn't match the betas... maybe because of - scaling
with latitude and with ecosystem type?]] Scaling of $G$ with the proportion of
top predators did not vary across latitude. Scaling was strongest in stream
ecosystems ($\alpha_{Stream}$=-0.344, $p$\textless0.001) and weakest in marine
food webs ($\alpha_{Marine}$=0.170, $p$=0.008).

Scaling of $V$ with $S$ was slightly stronger towards the equator
($\alpha_{Latitude}$=-0.001, $p$=0.267; Fig.~\ref{}) except in lake food webs
where scaling was stronger towards the poles ($\alpha_{Latitude:Lake}$=0.005,
$p$=0.008). When scaling was broken up by trophic level, however, lake food
webs were not so exceptional. Scaling of $V$ with $B$ was stronger towards the
poles in estuarine, lake and stream food webs ($\alpha_{Latitude}$=-0.007,
$p$=0.006). This trend was reversed for marine and terrestrial food webs
($\alpha_{Latitude:Marine}$=0.009, $p$=0.047;
$\alpha_{Latitude:Terrestrial}$=0.013, $p$=0.002). Scaling of $V$ with $I$ was
not affected by latitude in any ecosystem type.  Scaling of $V$ with $T$ was
slightly stronger towards the equator in estuarine, marine, and lake food webs
($\alpha_{Latitude}$=-0.001, $p$=0.521) but stronger towards the equator in
stream and terrestrial food webs ($\alpha_{Latitude:Stream}$=0.015,
$p$\textless0.001; $\alpha_{Latitude:Terrestrial}$=0.006, $p$=0.067).

>>>>

$Z$, $G$, and $V$ all increased with increasing $S$ at all latitudes. The strength of
this increase varied both over latitude and across ecosystem types. For $Z$,
scaling was stronger towards the equator in estuarine, marine, stream, and
terrestrial ecosystems (). In lake ecosystems, however, scaling was stronger
toward the poles. $G$ and $V$ followed the same trends, except that scaling of $G$
with $S$ was stronger towards the poles as in lakes ().

When considering the proportion of $S$ accounted for by different trophic
levels, however, the scaling relationships with $Z$, $G$, and $V$ were more
complex. While $Z$ increased with increasing $I$ as well as with increasing
$S$, $Z$ tended to decrease with increasing $B$ and $T$. The decrease of $Z$
with $B$ was stronger towards the poles in estuarine, lake, and stream webs
(), varied little over latitude in marine webs (), and was stronger towards
the poles in terrestrial webs (). The best-fitting model for the relationship
of $Z$ and $I$ did not include any terms for variation in scaling across
latitude for any ecosystem type. Similar to the scaling of $Z$ with $B$, the
decrease in $Z$ with increasing $T$ was stronger towards the poles in
estuarine, lake, and marine webs, although the influence of latitude was
weaker than with $B$ (). Again like the relationship between $Z$ and $B$,
scaling of $Z$ with $T$ was stronger towards the equator in terrestrial webs.
Unlike in the relationship between $Z$ and $B$, however, scaling of $Z$ with
$T$ was also stronger towards the equator in stream webs.

As with $Z$, $G$ tended to decrease with increasing $B$ and $T$ and increase
with increasing $I$. Once again, however, these trends varied with latitude
and ecosystem type. The decline of G with increasing S was strongest at the
poles in estaurine, lake, and marine ecosystems; in each ecosystem type $G$
increased slightly with $B$ in equatorial webs. In marine webs $G$ increased
slightly with $B$ at all latitudes and in terrestrial webs $G$ increased with
$B$ in high-latitude webs but decreased slightly with $B$ at the equator. The
strength of the increase in $G$ with $I$ varied little with latitude except in
stream webs, where the increase was strongest towards the equator and $G$
decreased with $I$ in arctic food webs. The best-fitting model for the scaling
of $G$ with $T$ did not include any terrms for latitude in any ecosystem type.

$V$ too generally decreased with increasing $B$ and $T$ while increasing with
$I$. Similar to $G$, the decline of $V$ with increasing $B$ was strongest
towards the poles in estuarine, lake, and stream webs, varied little with
latitude in marine webs, and was strongest towards the equator in terrestrial
food webs. As with $Z$, the best-fit model for the scaling of $V$ with $I$ did
not include any terms for latitude in any ecosystem type. Scaling of $V$ with
$T$ was also simmilar to the pattern for $Z$, with sharper decreases in $V$
towards the poles in estuarine, lake, and marine webs and stronger towards the
equator in terrestrial and stream webs.
